Accountants' Attitudes Towards Open Science

### 2024-04-17 docs/presentation.qmd
Added observational data analyses

---
title: "Accountants' Attitudes Towards Open Science"
author: Joachim Gassen, Jacqueline Klug, and Victor van Pelt
institute: "HU Berlin and WHU – Otto Beisheim School of Management"
date: "`r format(Sys.time(), '%B %d, %Y')`"
format: 
  beamer: 
    latex_engine: xelatex # pdflatex creates rastered fonts
    slide_level: 3
classoption: "aspectratio=169"
bibliography: references.bib

@@

sd <- readRDS("../data/generated/survey_response.rds")
mr <- readRDS("../data/generated/merged_response.rds")
vars <- read_csv("../data/external/variables.csv", show_col_types = FALSE)
pop <- read_csv(
	"../data/external/invited_authors_retracted.csv", show_col_types = FALSE
)

@@

```{r Tab4aReprMethod, asis = TRUE}
tab <- create_pct_cross_tab_table(
	sd, "reprod_acc", "demog_method", 
	ctests = TRUE, df_only = TRUE
)

gt(tab %>% select(-Other)) %>% 
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()

@@

```{r Tab4cReprMethod, asis = TRUE}
sd$reprod_method_delta <- as.numeric(sd$reprod_method) - as.numeric(sd$reprod_acc)
tab <- create_pct_cross_tab_table(
	sd, "reprod_method_delta", "demog_method", 
	resp_label = sort(na.omit((unique(sd$reprod_method_delta)))),
	ctests = TRUE, add_num_labels = FALSE, df_only = TRUE 
) 
gt(tab %>% select(-Other)) %>%
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()
```

@@

```{r Tab6bSharingImportance, asis = TRUE}
df <- sd %>% filter(demog_method != "Other")
tab <- create_pct_cross_tab_table(
	df, "sharing_important", "demog_method", 
	ctests = TRUE, df_only = TRUE
) 
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()
```

@@

@@

```{r Figure4, fig.width=8, fig.height=3.5, fig.align="center", fig.showtext = TRUE}
p <- pre_reg_over_time_plot(mr) + theme(legend.position = "right") 
if (trr266_fonts_available) {
	p + theme(text = element_text(family = "Calibri Light", size = 7))
} else p

@@

```{r Tab11aPreRegFamiliarity, asis = TRUE}
df <- sd %>% filter(demog_method != "Other")
tab <- create_pct_cross_tab_table(
	df, "prereg_familiar", "demog_method", 
	ctests = TRUE, df_only = TRUE
) 
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()
```

@@

tab <- create_pct_cross_tab_table(
	df, "prereg_use", "demog_method", 
	resp_label = c("No (0)", "Yes (1)"), 
	add_num_labels = FALSE, ctests = TRUE, df_only = TRUE
) 
# Adjust levels to be zero based.
tab[4,2:6] <- t(sprintf("%.2f", as.numeric(tab[4,2:6]) - 1))
tab[5,2:6] <- t(sprintf("%.2f", as.numeric(tab[5,2:6]) - 1))
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()
```

@@

tab <- create_pct_cross_tab_table(
	df, "prereg_trust", "demog_method", 
	ctests = TRUE, df_only = TRUE
) 
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()
```

>>>>

---
title: "Accountants' Attitudes Towards Open Science"
subtitle: "" # we use this for the venue
author: Joachim Gassen, Jacqueline Klug, and Victor van Pelt
institute: "HU Berlin and WHU – Otto Beisheim School of Management"
date: today
date-format: "MMMM D, YYYY"
format: 
  beamer: 
    latex_engine: xelatex # pdflatex creates rastered fonts
    slide_level: 3

classoption: "aspectratio=169"
bibliography: references.bib

@@

sd <- readRDS("../data/generated/survey_response.rds")
mr <- readRDS("../data/generated/merged_response.rds")
vars <- read_csv("../data/external/variables.csv", show_col_types = FALSE)
pop <- read_csv(
	"../data/external/invited_authors_anon.csv", show_col_types = FALSE
)

authors <- read_csv("../data/external/obs_data_authors_anon.csv", show_col_types = FALSE)
papers <- read_csv("../data/external/obs_data_papers_anon.csv", show_col_types = FALSE)

source("../code/obs_data_analyses.R")

@@

```{r Tab4aReprMethod, asis = TRUE}
tab <- create_pct_cross_tab_table(
	sd, "reprod_acc", "demog_method", include_total = TRUE,
	drop_levels = "Other", ctests = TRUE, df_only = TRUE
)

gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()

@@

```{r Tab4cReprMethod, asis = TRUE}
sd$reprod_method_delta <- as.numeric(sd$reprod_method) - as.numeric(sd$reprod_acc)
tab <- create_pct_cross_tab_table(
	sd, "reprod_method_delta", "demog_method", include_total = TRUE,
	drop_levels = "Other", 
	resp_label = sort(na.omit((unique(sd$reprod_method_delta)))),
	ctests = TRUE, add_num_labels = FALSE, df_only = TRUE 
) 
gt(tab) %>%
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()
```

@@

```{r Tab6bSharingImportance, asis = TRUE}
tab <- create_pct_cross_tab_table(
	sd, "sharing_important", "demog_method", include_total = TRUE,
	drop_levels = "Other", ctests = TRUE, df_only = TRUE
) 
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()
```

@@

## Observational Data on Sharing Behavior: Author Level

```{r, asis = TRUE}
gt(tab_by_author) %>% 
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()
```

## Observational Data on Sharing Behavior: Journal Level

```{r, asis = TRUE}
gt(tab_by_journal) %>% 
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()
```

## Observational Data: Paper-level Sharing over Time

```{r Figure4, fig.width=8, fig.height=3.5, fig.align="center", fig.showtext = TRUE}
p <- plot_resmat_sharing_over_cyear
if (trr266_fonts_available) {
	p + theme(text = element_text(family = "Calibri Light", size = 12))
} else p
```

@@

```{r Figure5, fig.width=8, fig.height=3.5, fig.align="center", fig.showtext = TRUE}
p <- pre_reg_over_time_plot(mr) + theme(legend.position = "right") 
if (trr266_fonts_available) {
	p + theme(text = element_text(family = "Calibri Light", size = 12))
} else p

@@

```{r Tab11aPreRegFamiliarity, asis = TRUE}
tab <- create_pct_cross_tab_table(
	sd, "prereg_familiar", "demog_method", include_total = TRUE,
	drop_levels = "Other", 
	ctests = TRUE, df_only = TRUE
) 
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()
```

@@

tab <- create_pct_cross_tab_table(
	sd, "prereg_use", "demog_method", include_total = TRUE,
	drop_levels = "Other", resp_label = c("No (0)", "Yes (1)"), 
	add_num_labels = FALSE, ctests = TRUE, df_only = TRUE
) 
# Adjust levels to be zero based.
tab[4,2:7] <- t(sprintf("%.2f", as.numeric(tab[4,2:7]) - 1))
tab[5,2:7] <- t(sprintf("%.2f", as.numeric(tab[5,2:7]) - 1))
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()
```

@@

tab <- create_pct_cross_tab_table(
	sd, "prereg_trust", "demog_method", include_total = TRUE,
	drop_levels = "Other", ctests = TRUE, df_only = TRUE
) 
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()
```
